A Study on Penguins: A Minimal Reproducible Example

### 2024-08-23 01_Example/Manuscript.qmd
Use flextable rather than tinytable
to allow referencing tables
see https://github.com/wjschne/apaquarto/issues/83

Descriptive statistics of the data set are displayed in Table 1.

```{r}
#| label: "descriptive-statistics"
#| echo: false
#| tbl-cap: "Descriptive Statistics"

within(dat, {
  sex[is.na(sex)] <- "unknown"
  year <- as.factor(year) # Year is more interesting if analyzed as factor
}) |>
  (\(x) { # Add number of non-missings
    n <- sapply(x, \(v) sum(!is.na(v)))
    labels <- paste0(names(x), " (N=", n, ")")
    idx <- which(sapply(x, is.numeric))
    names(x) <- names(x) |>
      replace(
        list = idx,
        values = labels[idx]
      )
    x
  })() |>
  modelsummary::datasummary_balance(formula = ~ sex, dinm = FALSE) |>
  tinytable::style_tt(
    # Make table more compact to fit on page
    tabularray_inner = "rowsep={0.2em}, colsep = {0.2em}"
  )

>>>>

Descriptive statistics of the data set are given in @tbl-descriptive-statistics and individual bill lengths are displayed in @fig-bill-length-comparison.

```{r}
#| label: "tbl-descriptive-statistics"
#| echo: false
#| tbl-cap: "Descriptive Statistics"
#| apa-twocolumn: true

within(dat, {
  sex[is.na(sex)] <- "unknown"
  year <- as.factor(year) # Year is more interesting if analyzed as factor
}) |>
  (\(x) { # Add number of non-missings
    n <- sapply(x, \(v) sum(!is.na(v)))
    labels <- paste0(names(x), " (N=", n, ")")
    idx <- which(sapply(x, is.numeric))
    names(x) <- names(x) |>
      replace(
        list = idx,
        values = labels[idx]
      )
    x
  })() |>
  modelsummary::datasummary_balance(formula = ~ sex, output = "flextable", dinm = FALSE) |>
  flextable::theme_apa() |>
  flextable::font(fontname = "TeX Gyre Termes", part = "all")
